Final Project Draft #2

### 2022-04-27 draft2.Rmd
switched the axis

GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(y = GDPPC, x = `Hours Worked`, color = `City`)) +
  geom_point() +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       caption = "Data from: ADD LATER",
       y = "GDP per capita (USD)",
       x = "Hours Worked (Weekly)",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "lightblue",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))

>>>>

GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
  geom_point() +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       caption = "Data from: ADD LATER",
       x = "GDP per capita (USD)",
       y = "Hours Worked (Weekly)",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "lightblue",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))
